Fast, Scalable Phrase-Based SMT Decoding

### 2016-03-10 acl.2016/acl2016.tex
nikolay ref

For any realistic sized phrase-based model to be used in an online situation, memory and loading time constraints requires us to use load-on-demand phrase-table implementations. Moses contains a number of such implementations with different performance characterics, we show the time take to decode 800,000 sentences for the fastest two in Figure~\ref{fig:moses-phrase-tables-time}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding time with two different phrase-table implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
From this, it appears that the Probing phrase-table~\cite{Bogochev:Thesis:2013} has the fastest translation rule lookup, especially with large number of cores, therefore, we will concentrate exclusively on this implementation in our work as this . We will look at two main areas for phrase-table optimization specifically in relation to the Probing implementation.

>>>>

For any realistic sized phrase-based model to be used in an online situation, memory and loading time constraints requires us to use load-on-demand phrase-table implementations. Moses contains a number of such implementations with different performance characterics, we show the time take to decode 800,000 sentences for the fastest two in Figure~\ref{fig:moses-phrase-tables-time}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding time with two different phrase-table implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
From this, it appears that the Probing phrase-table~\cite{Bogoychev:Thesis:2013} has the fastest translation rule lookup, especially with large number of cores, therefore, we will concentrate exclusively on this implementation in our work as this . We will look at two main areas for phrase-table optimization specifically in relation to the Probing implementation.
